WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-12-26 lit/sec_3-other-systems.tex
Revised MSM Lit

Meta Scientific Modeling framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents. Even these features are provided by other systems such as Delft-FEWS, they do not provide decentralized model execution and data integration. Specifically, this framework provides a graphical user interface for workflow creation similar to LEAD, rather than providing a configuration-based workflow system similar to Delft-FEWS. During our research we are not mainly focusing on implementing a workflow engine, we will not very much look into such features here.
Then MSM tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitates users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the MSM framework.

@@

\cref{fi:msm_architecture} shows the MSM system framework from a top-level design point of view, and it mainly composed of the MSM core which is an interface with the workflow engine, data agents, and model agents. Thus, the MSM core can become the bottleneck of the system, and a single point of failure in critical situations. The MSM core also controls all other components and by using corresponding model agents and data agents allows to connect with external models and remote data sources. The MSM core is connected to the workflow engine and provides the end-user with all workflow control capabilities, and it contains data persistence services that can be used by all MSM components. Another drawback is, implementing new data agents and model agents are programming language-dependent. In order to implement Model Agents and Data agents, users need to inherit MSM classes in the provided language. Then users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).

The open-data architecture of MSM is using for access multiple and heterogeneous external data sources. The users able to integrate data from any source via data agents, but the data agents are depending on inheriting a genric class to do so. Which means there is a language dependency. The open model architecture allow users to independently develop and deploy own model via model agents. Here also users have to use a genric agent provided by the MSM framework, but the models can be implemented independently. Users can deploy new model agents by copy pasting the source code to a specific folder, but it is possible to run the models which can be written in C, C++, Fortran, Python, Java, etc. During the model execution, it follow a flow similar to the Delft-FEW model adapter with prepare input file, execute the model, and processing output files. The MSM framework has a data management layer, which store the data as an inmemory and local data caching, featuring a non-relational database scheme that supports high throughput. It stores particular timeseries data as msmDataSets, and create unique identifier for each msmDataSet. 
The msmDataSets storage in framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.

In this paper, it present a use case of using the MSM system, and does not provide detailed evaluation regarding a performance load testing. In this use case, it demonstrates the usefulness and effectiveness of the framework in various aspects of scientific modeling activities. The msm has only been fully tested on Windows 10 operating system, which means the framework has some operating system dependency. Further, It is not very clear how is it parallel running data agents, model agents, and the MSM core. Even it mentioned it follow the decentralized agents approach, based on the available data we can conclude it also have a monolithic distributed architecture.

>>>>

\acrfull{msm} framework develops an open system architecture which consists of open-data concept to access heterogeneous data sources via data agents, and open-model concept to allow individual model handling via model agents. Even through these features are provided by other systems such as \acrshort{fews}, they do not provide decentralized model execution and data integration. Specifically, this framework provides a graphical user interface for workflow creation similar to \acrshort{lead}, rather than providing a configuration-based workflow system as in \acrshort{fews}. In our research, we are not mainly focusing on implementing a workflow engine, we will not look deep into such features here.
Then \acrshort{msm} tries to effectively address the drawbacks of the existing modeling systems by providing features such as an independent open-source and graphical-based workflow engine, facilitating  users to obtain data directly from popular sources, decentralized model administration by modelers, and enables models to be freely connected with each other in the \acrshort{msm} framework.

@@

\cref{fi:msm_architecture} shows the \acrshort{msm} system framework from a top-level design point of view, and it is mainly composed of the \acrshort{msm} core which is an interface with the workflow engine, data agents, and model agents. Thus, the \acrshort{msm} core can become the bottleneck of the system, and a single point of failure in critical situations. The \acrshort{msm} core also controls all other components and by using corresponding model agents and data agents allows it to connect with external models and remote data sources. The \acrshort{msm} core is connected to the workflow engine and provides the end-user with all workflow control capabilities, and it contains data persistence services that can be used by all \acrshort{msm} components. Another drawback is, implementing new data agents and model agents are programming language-dependent. In order to implement Model Agents and Data agents, users need to inherit \acrshort{msm} classes in the provided language. Then users need to upload the code into a folder (not a containerized mechanism, or continuous service deployments).

The open-data architecture of \acrshort{msm} is using to access multiple and heterogeneous external data sources. The users are able to integrate data from any source via data agents, but the data agents are depending on inheriting a generic class to do so. Which means there is a language dependency. The open model architecture allows users to independently develop and deploy their own model via model agents. Here also users have to use a generic agent provided by the \acrshort{msm} framework, but the models can be implemented independently. Users can deploy new model agents by copy pasting the source code to a specific folder, but it is possible to run the models which can be written in C, C++, FORTRAN, Python, Java, etc. During the model execution, it follows a flow similar to the Delft-FEW model adapter with a prepared input file, execute the model, and processing output files. The \acrshort{msm} framework has a data management layer, which stores the data as an in memory and local data caching, featuring a non-relational database scheme that supports high throughput. It stores particular timeseries data as msmDataSets, and creates a unique identifier for each msmDataSet. 
The msmDataSets storage framework contains the time-steps. Each time-step contains a reference to the msmDataSet it belongs to, and a Document (the data oriented structure) with a 2D image.

In this paper, it presents a use case of using the \acrshort{msm} system, and does not provide detailed evaluation regarding a performance load testing. In this use case, it demonstrates the usefulness and effectiveness of the framework in various aspects of scientific modeling activities. The msm has only been fully tested on Windows 10 operating system, which means the framework has some operating system dependency. Further, It is not very clear how is it parallel running data agents, model agents, and the \acrshort{msm} core are. Even though it mentioned it follows the decentralized agents approach, based on the available data we can conclude it also has a monolithic distributed architecture.
